\ability%
    {Blood-Magic Conversion}
    {Battlemage Ability}
    {1 bonus action}
    {Self}
    {Instantaneous}
    {1 per long rest}
Your very life-blood recharges your magical reserves
in moments of great need.
Whenever you are bloodied (equal to or below half hit point maximum),
you may use a bonus action to take $x$d12 force damage
and regain a spell slot of $x$-th level.

You may use this ability again once you finish a long rest.


\ability%
    {Closing Statement}
    {Battlemage Ability}
    {On condition}
    {See text}
    {Instantaneous}
    {1 per long rest}
You've saved the best for last.
Whenever you use your last remaining $n$-th level spell slot,
you may use this ability to overcharge the spell cast with that slot.
Any damage dealt by the spell uses \textbf{exploding dice}.
When you roll the maximum value on an exploding die,
you may roll that die again.
If the result is the maximum again,
you roll the die a further time,
and so on until the maximum has no longer been rolled.

You may use this ability again once you finish a long rest.


\ability%
    {Defence Against the Old Way}
    {Battlemage Ability}
    {Dependent on the power, see text}
    {As above}
    {As above}
    {1 per long rest}
Accompanied with your study of the Old Way is the knowledge
of how to defend against its malign affects. You may manifest
either the \power{detect psionics} or \power{mind palace} power
as a 1/day innate talent. Once you manifest either, you may not
use this ability again until you finish a long rest.

\ability%
    {Half-remembered Lecture}
    {Battlemage Ability}
    {1 minute of concentration}
    {Self}
    {Until you finish a long rest}
    {1 per long rest}
The need of the hour has called to mind
a near-forgotten lecture from your time at the College.
If you spend one minute, in which you continuously use your action
to maintain concentration on this ability,
you may replace one spell on your list of prepared spells
with any spell from the wizard class list.
That spell counts as being prepared.

Once you finish a long rest,
the spell you learnt with this ability is forgotten
and the original spell restored to your list of prepared spells.


\ability%
    {Keeper of Arcane Secrets}
    {Battlemage Ability}
    {1 reaction, which you take whenever you fail an applicable check}
    {See text}
    {Instantaneous}
    {1 per long rest}
Your preside over an impressive mental store
of arcane lore and knowledge.
Whenever you fail an Intelligence (Arcana) check
or fail an Intelligence (Investigation) check relating
to a magical item, creature or effect,
you may use your reaction to instead succeed on the check.

You may use this ability again once you finish a long rest.


\ability%
    {Psionic Awakening}
    {Battlemage Ability}
    {1 action}
    {30 feet}
    {Concentration, up to 1 minute}
    {2 per day}
Your intense but brief study of the Old Way has awakened
latent psionic abilities within you. Your may manifest
the \power{matter agitation} psionic power as a 2/day innate talent.


