\ability%
    {"Live Rightly, Die, Die"}
    {Fukasawa Vassal Ability}
    {1 reaction}
    {Self}
    {Instant}
    {Once per day}
When you are reduced to 0 hit points,
if your Sirisean renown is greater than 3,
you may use your reaction to
instead be reduced to 1 hit point.

Then, pick a number between 1 and 6.
Multiply this number by 5.
This is the DC for a Charisma (Persuasion) check
as you send a prayer to any good-aligned spirits or aspects.
If the check is successful,
you may immediately roll a number of d8s equal to
the number you picked.
An enemy of your choosing then takes this amount
in radiant damage.

You can use this ability once per day.


\ability%
    {Honour unto Death}
    {Fukasawa Vassal Ability}
    {1 bonus action}
    {Self}
    {1d4 rounds (or 0 hp); see text}
    {Once per long rest}
When you become \textbf{bloodied}
(below half hit point maximum),
your bond to Sirisean codes of honour---or
legends of martial prowess---compel you to fight on.

You may use your bonus action to gain resistance
to one damage type of your choosing for 1d4 rounds,
or until you drop to 0 hit points.

You can use this ability again once your complete a long rest.


\ability%
    {Moment of Clarity}
    {Fukasawa Vassal Ability}
    {On condition}
    {Self}
    {Instant}
    {2 per dawn}
At critical moments---whether by the Divine Wind
or serendipitously---you gain a moment of clarity
which you can use to your advantage.

Once per day,
you may add the result of 1d4 to any roll you make.
You can use this ability twice per dawn.


\ability%
    {Rose of Fukasawa}
    {Fukasawa Vassal Ability}
    {1 action}
    {10 feet}
    {1 minute}
    {Once per day}
If you possess this ability,
you gain access to the standard of Fukasawa---a
great banner bearing the Domain's sigil of a red rose.

Once per day as an action,
you may plant the standard at any point within 10 ft.
For one minute,
the standard becomes a beacon of hope, courage and duty.
Any clansman of Fukasawa within 20 ft. of the standard
cannot be frightened or charmed,
and they regain 1d8 hit points at the start of their turn.

Only one member per adventuring party can have
access to this ability and the Rose,
and it can only be used once per day.


\ability%
    {Selfless Courage}
    {Fukasawa Vassal Ability}
    {1 reaction}
    {5 feet; enemy's attack range; see text}
    {Instant}
    {3 per long rest}
\textit{The cry of distress is the summons to relief.}

When an ally takes damage from a spell or weapon attack,
you may use your reaction to either
(a) pass the damage onto yourself if you are within 5 ft.
of the ally,
or (b) intimidate the attacker.

If you choose to intimidate the attacker,
make a Charisma (Intimidation) check
contested by the target's passive Wisdom (Insight).
If you succeed,
the target can no longer target that ally
until the start of their next turn.

You can use this ability 3 times per long rest.


\ability%
    {Smite Thine Enemy}
    {Fukasawa Vassal Ability}
    {Reaction}
    {Melee or ranged weapon reach}
    {Instant}
    {Once per Bastion turn}
If you land a melee or ranged weapon attack against a creature,
and they are an enemy of the Fukasawa Domain,
you may as a reaction to imbue your attack with unrelenting power.

If you do so,
the targeted creature must make a Charisma saving throw
with DC equal to 8 + your Charisma modifier
+ your proficiency bonus.
If they fail the save,
the damage dice are tripled for that attack.

\ability%
    {Unyielding Presence}
    {Fukasawa Vassal Ability}
    {1 bonus action}
    {Self}
    {1 minute}
    {Once per long rest}
Danger and seemingly insurmountable threats
do not dishearten you.
You may use your bonus action to gain immunity
to the frightened condition for 1 minute.

You may use this ability again after completing a long rest.


\ability%
    {Wrath of the Silvered}
    {Fukasawa Vassal Ability}
    {1 action}
    {30 feet}
    {1d4 rounds}
    {Once per day}
Once per day,
you call upon the wrath of Yamataka the Silvered---Custodian
of Fukasawa---to engender fear in your enemies.

As an action,
choose one target within 30 feet.
If they fail a DC 14 Wisdom saving throw,
they become vulnerable to damage from silvered weapons
or anything silver in make.
This lasts for 1d4 rounds.


