\ability%
    {Batter Them Down!}
    {Hammer Militia Ability}
    {1 reaction, which you take when an enemy creature in your reach is knocked prone}
    {Melee reach}
    {Instantaneous}
    {3 per long rest}
When an enemy creature within your melee reach is knocked prone,
you may use your reaction to keep them that way. 
Make one melee attack against the creature
that was knocked prone.
If the attack deals damage,
the creature must also make a Constitution saving throw
with DC equal to half the damage you dealt.
If the creature fails the save,
they are incapacitated until the end of their next turn.

You may use this ability 3 times per long rest.


\ability%
    {Body Block}
    {Hammer Militia Ability}
    {1 bonus action}
    {Melee reach}
    {Until the grapple ends}
    {3 per long rest}
Your experience fighting in large crowds
has honed your ability to use the environment---including
other people---to your advantage.
You may use a bonus action to attempt to grapple a creature,
making the relevant check with advantage.
If the grapple is successful,
until the grapple ends,
you always have three-quarters cover.
In addition,
you can always take the hide action even though enemy creatures
have line of sight towards you.


\ability%
    {Hamstring Shot}
    {Hammer Militia Ability}
    {1 action}
    {Ranged attack range}
    {Instantaneous}
    {3 per long rest}
You target your enemy with a precision shot,
greatly hampering their movement.
Make a ranged weapon attack with any ranged weapon available
as part of this action.
If the attack hits,
the target must make a Constitution saving throw
with DC equal to 8 + your ranged weapon attack modifier.
If the target fails,
the target's speed is halved until the end of your next turn.
When this speed reduction ends,
the target takes damage equal to four times your proficiency bonus.

\ability%
    {Pick Up the Slack!}
    {Hammer Militia Ability}
    {1 reaction}
    {30 feet}
    {Instantaneous}
    {2 per long rest}
Your training has encouraged you to step in for your allies,
covering their failures with your success.
Whenever an ally within 30 feet of you fails an ability check
but before the outcome is decided,
you may use a reaction to repeat the check yourself.
Use your relevant ability modifier (not your ally's).
If the check is successful,
treat the ally's original check as if it were successful.


\ability%
    {Pop, Pop, Pop}
    {Hammer Militia Ability}
    {1 action}
    {20-foot cone}
    {Instantaneous}
    {3 per long rest}
As an action,
you send forth a rapid barrage of thrown weapons,
such as throwing hammers, upon your enemies.
Each creature within a 30-foot cone centred on yourself
must make a Dexterity saving throw with DC equal to
8 + your thrown weapon attack modifier.

A creature that fails the save takes $x$d6 damage,
where $x$ is your proficiency bonus,
and is blinded until the end of your next turn.
A creature that succeeds the save takes half this damage
and is not blinded.
The damage type is the same as normal for the thrown weapons,
or, if multiple weapons with different damage types are thrown,
you may choose the type from the possible options.

You must have at least three thrown weapons on your person
to use this ability.
You can use this ability 3 times per long rest.


\ability%
    {Run Like Hell}
    {Hammer Militia Ability}
    {Free action}
    {Self}
    {Until the end of your turn}
    {Recharge 5-6; long rest}
At the start of your turn,
you may use a free action to prepare yourself
for an incredible burst of speed and agility,
leaving your enemies dazed and confused.

Whenever you move on that same turn,
every enemy creature that can make an opportunity attack
against you as a result of this movement
instead attacks itself with its opportunity attack.
Each enemy must make this opportunity attack;
they cannot willingly forego the attack to
avoid taking damage.

At the end of combat, roll 1d6.
This ability recharges if you roll a 5 or greater.
Otherwise, it recharges after a long rest.


\ability%
    {Strength in Numbers}
    {Hammer Militia Ability}
    {Free action}
    {Self}
    {Until the end of your turn, see text}
    {3 per long rest}
If you are adjacent to at least one allied creature,
you may use a free action to cut deeper into your enemies,
exploiting lapses in their attention.
Until the end of your current turn
or until you are no longer adjacent to any allied creatures
(whichever is sooner),
you may add your proficiency bonus to your damage rolls.


